---
title: "Symbiodiniaceae ITS2 analysis of coral juveniles produced from selective breeding (AGF)- Seasim lab experiments"
output: html_document
---


# This pipeline processes ITS2 sequencing data to analyse the Symbiodiniaceae community composition in corals. 
#The full original pipeline used is available on: #https://github.com/LaserKate/MontiSymTransgen/blob/master/DADA2analysis_DESeq.R 

#and published: 
#Transgenerational inheritance of shuffled symbiont communities in the coral Montipora digitata
#Kate M. Quigley, Bette L. Willis & Carly D. Kenkel 
#Scientific Reports volume 9, Article number: 13328 (2019) 
#https://www.nature.com/articles/s41598-019-50045-y

#Kat Damjanovic also added some nice front-end bit to help clean-up sequences and prep reads for processing and added the Venn diagram code

# Before starting R analysis, the following commands run in the Terminal:

# 1) Unzipping the files, type:
# gunzip *.gz

# 2) "Some pre-trimming. Retain only PE reads that match amplicon primer".
#    "Remove reads containing Illumina sequencing adapters":

# ls *R1_001.fastq | cut -d '_' -f 1 > samples.list

# for file in $(cat samples.list); do  mv ${file}_*R1*.fastq ${file}_R1.fastq; mv ${file}_*R2*.fastq ${file}_R2.fastq; done 

#for file in $(cat samples.list); do bbduk.sh in1=${file}_R1.fastq in2=${file}_R2.fastq ref=adaptors.fasta k=12 out1=${file}_R1_NoIll.fastq out2=${file}_R2_NoIll.fastq ; done &>bbduk_NoIll.log

#for file in $(cat samples.list); do bbduk.sh in1=${file}_R1_NoIll.fastq in2=${file}_R2_NoIll.fastq restrictleft=21 k=10 literal=GTGAATTGCAGAACTCCGTG,CCTCCGCTTACTTATATGCTT outm1=${file}_R1_NoIll_NoITS.fastq outu1=${file}_R1_check.fastq outm2=${file}_R2_NoIll_NoITS.fastq outu2=${file}_R2_check.fastq; done &>bbduk_NoITS.log


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Call libraries

```{r calling libraries}
library(dada2); packageVersion("dada2"); citation("dada2")
library(ShortRead); packageVersion("ShortRead")
library(ggplot2); packageVersion("ggplot2")
library(phyloseq); packageVersion("phyloseq")
library(dplyr)
library(vegan)

setwd("")

```


# ################################## Start of DADA analysis ##################################

```{r defining paths, echo=FALSE}

# Set path to trimmed, renamed fastq files
# Folder where unzipped, trimmed and renamed data are stored:

path <- "ITS2_test_data"
fns <- list.files(path)
fns

```


##### Trimming/Filtering #######

```{r sorting reads, echo=FALSE}

fastqs <- fns[grepl(".fastq$", fns)]
fastqs <- sort(fastqs) # Sort ensures forward/reverse reads are in same order
fnFs <- fastqs[grepl("_R1", fastqs)] # Just the forward read files
fnRs <- fastqs[grepl("_R2", fastqs)] # Just the reverse read files

```


##### Get sample names, assuming files named as so: SAMPLENAME_XXX.fastq; OTHERWISE MODIFY #######

```{r specifying paths, echo=FALSE}

sample.names <- sapply(strsplit(fnFs, "_"), `[`, 1) #the last number will select the field for renaming
# Specify the full path to the fnFs and fnRs
fnFs <- file.path(path, fnFs)
fnRs <- file.path(path, fnRs)

```

#### Visualize Raw data #######

```{r quality plots, echo=FALSE}

#First, lets look at quality profile of R1 reads
 
plotQualityProfile(fnFs[c(1,2,3,4)]) 
plotQualityProfile(fnFs[c(88,89,90,91)])

# The quality for forward reads drops at about 280 bp

#Then look at quality profile of R2 reads

quartz()
plotQualityProfile(fnRs[c(1,2,3,4)])
plotQualityProfile(fnRs[c(88,89,90,91)])

# The quality for forward reads drops at about 260 bp (quality worse than forward reads, as per usual)

# "DADA2 incorporates quality information into its error model which makes the algorithm more robust,
# but trimming as the average qualities crash is still a good idea as long as our reads will still overlap. 
# For Pochon ITS2 primers, have 160 bp overlap. Can trim quite a bit"


# "The distribution of quality scores at each position is shown as a grey-scale heat map,
# with dark colors corresponding to higher frequency. Green is the mean, orange is the median,
# and the dashed orange lines are the 25th and 75th quantiles.
# Recommend trimming where quality profile crashes - in this case, forward reads mostly fine up to 270-280;
# for reverse >220-230 bases it gets below 30; this leaves enough overlap"

# "If using this workflow on your own data: Your reads must still overlap after truncation in order to merge
# them later! If you are using a less-overlapping primer set, your truncLen must be large enough to maintain
# 20 + biological.length.variation nucleotides of overlap between them.
# BUT: For common ITS amplicon strategies, it is undesirable to truncate reads to a fixed length due to
# the large amount of length variation at that locus. That is OK, just leave out truncLen.
# Make sure you removed the forward and reverse primers from both the forward and reverse reads though! 
# Not too many indels in ITS2; at least not super long ones"

```


#### Filtering ####

```{r filtering, echo=FALSE}
# Make directory and filenames for the filtered fastqs

filt_path <- file.path(path, "trimmedSubTest")
if(!file_test("-d", filt_path)) dir.create(filt_path)
filtFs <- file.path(filt_path, paste0(sample.names, "_F_filt.fastq.gz"))
filtRs <- file.path(filt_path, paste0(sample.names, "_R_filt.fastq.gz"))


# Filter

# DADA does not allow Ns
# Allow 1 expected errors, where EE = sum(10^(-Q/10)); more conservative, model converges
# N nucleotides to remove from the start of each read: ITS2 primers = F 20bp; R 21bp
# remove reads matching phiX genome
# enforce matching between id-line sequence identifiers of F and R reads
# On Windows set multithread=FALSE

out <- filterAndTrim(fnFs, filtFs, fnRs, filtRs, truncLen=c(270,220),
              maxN=0, 
              maxEE=c(1,1), 
              truncQ=2, 
              trimLeft=c(20,21),  
              rm.phix=TRUE, 
              matchIDs=TRUE, 
              compress=TRUE, multithread=TRUE) 

# Warning message: Some input samples had no reads pass the filter

head(out) 
tail(out)

```


#### Learn Error Rates #######

```{r error rates, echo=FALSE}

# "DADA2 learns its error model from the data itself by alternating estimation of the error rates and
# the composition of the sample until they converge on a jointly consistent solution
# (this is similar to the E-M algorithm)
# As in many optimization problems, the algorithm must begin with an initial guess, for which the maximum
# possible error rates in this data are used (the error rates if only the most abundant sequence
# is correct and all the rest are errors)."

setDadaOpt(MAX_CONSIST=30) #increase number of cycles to allow convergence
errF <- learnErrors(filtFs, multithread=TRUE)

errR <- learnErrors(filtRs, multithread=TRUE)


# "sanity check: visualize estimated error rates
# error rates should decline with increasing qual score
# red line is based on definition of quality score alone
# black line is estimated error rate after convergence
# dots are observed error rate for each quality score"

plotErrors(errF, nominalQ=TRUE) 
plotErrors(errR, nominalQ=TRUE) 

# See comments on github link! Much more information is provided there.

```

##### Dereplicate reads #######

```{r dereplicate reads, echo=FALSE}

# "Dereplication combines all identical sequencing reads into into “unique sequences” with a corresponding
# “abundance”: the number of reads with that unique sequence. 
# Dereplication substantially reduces computation time by eliminating redundant comparisons.
# DADA2 retains a summary of the quality information associated with each unique sequence. The consensus quality
# profile of a unique sequence is the average of the positional qualities from the dereplicated reads.
# These quality profiles inform the error model of the subsequent denoising step,
# significantly increasing DADA2’s accuracy."

# Some samples were discarded during the trimming and filtering, so we should only select the existing ones:

exists <- file.exists(filtFs)
derepFs <- derepFastq(filtFs[exists], verbose=TRUE)
derepRs <- derepFastq(filtRs[exists], verbose=TRUE)

names(derepFs) <- sample.names[exists]
names(derepRs) <- sample.names[exists]


```

##### Infer Sequence Variants #######

```{r infere sequence variants, echo=FALSE}

# "Must change some of the DADA options b/c original program optomized for ribosomal data,
# not ITS - from github, "We currently recommend BAND_SIZE=32 for ITS data." leave as default for 16S/18S""

setDadaOpt(BAND_SIZE=32)

dadaFs <- dada(derepFs, err=errF, multithread=TRUE)
dadaRs <- dada(derepRs, err=errR, multithread=TRUE)

# "now, look at the dada class objects by sample
# will tell how many 'real' variants in unique input seqs
# By default, the dada function processes each sample independently, but pooled processing is available
# with pool=TRUE and that may give better results for low sampling depths at the cost of increased
# computation time. See our discussion about pooling samples for sample inference." 

dadaFs[[88]]
dadaRs[[88]]


```


##### Merge paired reads #######

```{r merge paired end reads, echo=FALSE}

# "To further cull spurious sequence variants
# Merge the denoised forward and reverse reads
# Paired reads that do not exactly overlap are removed"

mergers <- mergePairs(dadaFs, derepFs, dadaRs, derepRs, verbose=TRUE)

# Inspect the merger data.frame from the first sample
head(mergers[[88]])

summary((mergers[[88]]))

# "We now have a data.frame for each sample with the merged $sequence, its $abundance,
# and the indices of the merged $forward and $reverse denoised sequences. Paired reads that did not
# exactly overlap were removed by mergePairs.


```


##### Construct sequence table #######

```{r construct sequence table, echo=FALSE}

# "A higher-resolution version of the “OTU table” produced by classical methods

seqtab <- makeSequenceTable(mergers)
dim(seqtab) # 88 x 3042

# Inspect distribution of sequence lengths
table(nchar(getSequences(seqtab)))

plot(table(nchar(getSequences(seqtab)))) #real variants appear to be right in that 294-304 window

# "The sequence table is a matrix with rows corresponding to (and named by) the samples, and 
# columns corresponding to (and named by) the sequence variants. 
# Do merged sequences all fall in the expected range for amplicons? ITS2 Pochon ~340bp-41bp primers;
# accept 294-304
# Sequences that are much longer or shorter than expected may be the result of non-specific priming,
# and may be worth removing

seqtab2 <- seqtab[,nchar(colnames(seqtab)) %in% seq(294,304)] #again, being fairly conservative wrt length

table(nchar(getSequences(seqtab2)))
dim(seqtab2) # 88 x 1294


```


##### Remove chimeras #######

```{r remove chimeras, echo = FALSE}

# "The core dada method removes substitution and indel errors, but chimeras remain. 
# Fortunately, the accuracy of the sequences after denoising makes identifying chimeras easier 
# than it is when dealing with fuzzy OTUs: all sequences which can be exactly reconstructed as 
# a bimera (two-parent chimera) from more abundant sequences".

seqtab.nochim <- removeBimeraDenovo(seqtab2, method="consensus", multithread=TRUE, verbose=TRUE)
dim(seqtab.nochim) # 88 x 618: Identified 676 bimeras out of 1294 input sequences.

sum(seqtab.nochim)/sum(seqtab2) # 0.9837317

# "The fraction of chimeras varies based on factors including experimental procedures and sample complexity, 
# but can be substantial.
# BUT those variants account for only a minority of the total sequence reads
# Most of your reads should remain after chimera removal (it is not uncommon for a majority of sequence
# variants to be removed though)"

```

##### Track Read Stats #######

```{r track read stats, echo = FALSE}

getN <- function(x) sum(getUniques(x))
track <- cbind(out, sapply(dadaFs, getN), sapply(mergers, getN), rowSums(seqtab2), rowSums(seqtab.nochim))
colnames(track) <- c("input", "filtered", "denoised", "merged", "tabled", "nonchim")
rownames(track) <- sample.names
head(track)
tail(track)

write.csv(track,file="ReadFilterStats_SubsampledData.csv",row.names=TRUE,quote=FALSE)

```


##### Assign Taxonomy #######

```{r assign taxonomy, echo = FALSE}

# "It is common at this point, especially in 16S/18S/ITS amplicon sequencing, to classify
# sequence variants taxonomically. 
# DADA2 provides a native implementation of the RDP's naive Bayesian classifier. The assignTaxonomy function 
# takes a set of sequences and a training set of taxonomically classified sequences, and outputs the
# taxonomic assignments with at least minBoot bootstrap confidence.
# Quigley et al. 2019 use a modified version of the GeoSymbio ITS2 database (Franklin et al. 2012), but this is now uncurated.

#We have used the Arif 2014 database with modified synthax to suit assignTaxonomy
#Arif database also available on Github
#The ARIF database can be found as File S1 of that publication from 2014: https://onlinelibrary.wiley.com/doi/10.1111/mec.12869 (downloaded in 2018)



taxa <- assignTaxonomy(seqtab.nochim, "arif_ITS2_DB_mod.fasta", minBoot=5,multithread=TRUE,tryRC=TRUE,outputBootstraps=FALSE)
unname(head(taxa, 30))
unname(taxa)

# "Lowered bootstrap threshold from 50 to 5. Was not returning hits for many sequences. But reducing to 5
# improved sequence return and identities largely match separate blastn search against the same database"

# Now, save outputs so can come back to the analysis stage at a later point if desired
#saveRDS(seqtab.nochim, file="SubSam_seqtab_nochim.rds")
#saveRDS(taxa, file="SubSam_taxa_blastCorrected.rds")

```


# ################################## ##### handoff 2 phyloseq ####### ##################################

```{r import data and contruct phyloseq object}
##These are the original RDS files. They are listed here as a record but given they have data from other projects within them, I am not uploading 

#However, the subsetted samples for only this current AGF18 project is saved below and available: 
#psAGF
#saveRDS(psAGF, file="psAGF.rds")


# If you need to read in saved datafiles
#seqtab.nochim2 <- readRDS("SubSam_seqtab_nochim.rds") #has data from other projects in it.

#taxa2 <- readRDS("SubSam_taxa_blastCorrected.rds")
#taxa2 <- readRDS("SubSam_taxa_blastCorrected.rds") #has data from other projects in it.
#colnames(taxa2) <- "Species"

#import dataframe holding sample information
samdf<-read.csv("Juveniles_AGF18_Phyloseq_Metadata.csv")
head(samdf)
rownames(samdf) <- samdf$Samplename

# Construct phyloseq object...

# Sample names do not match! I rewrite the rownames of the ASV/OTU table so that "_F_filt.fastq.gz"
# is removed from the names of samples

#rownames1 <- rownames(seqtab.nochim2)
#rownames2 <- sub("_F.*", "", rownames1)
#rownames(seqtab.nochim2) <- rownames2

# Some samples are written as "1M1_1.1" in samdf but as "1M1-1-1" in seqtab.nochim2:

#rownames3 <- rownames(samdf)
#rownames4 <- chartr("._","--", rownames3)
#samdf$Samplename <- chartr("._","--", rownames4 <- chartr("._","--", rownames3))
#rownames(samdf) <- rownames4

# Some samples present in samdf are absent from seqtab.nochim2... I delete those 
#samdf2 <- samdf[order(row.names(samdf)), ] # alphabetical order according to row names so it matches table
#samdf3 <- subset(samdf2, (rownames(samdf2) %in% rownames(seqtab.nochim2))) # keep only common samples

# Three samples were discarded
#discarded <- subset(samdf2, !(Samplename %in% rownames(samdf3)))
#discarded # BkBkSST3H, CuBkD1T3H, SbBkD1T2A

# Construct phyloseq object (straightforward from dada2 outputs)
#ps <- phyloseq(otu_table(seqtab.nochim2, taxa_are_rows=FALSE), 
#               sample_data(samdf), 
#               tax_table(taxa2))
#ps

ITS2_AGF18_Ariftax_Edit<-read.csv("ITS2_AGF18_Ariftax_Edit.csv", row.names=1)
ITS2_AGF18_Ariftax_Edit.m<-as.matrix(ITS2_AGF18_Ariftax_Edit)
ITS2_AGF18_Ariftax_Edit.tax<-tax_table(ITS2_AGF18_Ariftax_Edit.m)

#ps.newtax <- phyloseq(otu_table(seqtab.nochim2, taxa_are_rows=FALSE), 
#               sample_data(samdf), 
#               tax_table(ITS2_AGF18_Ariftax_Edit.tax))

#should be 88 samples (AGF + Monti + Evo21)

# Summary of read counts - some samples have only 0 or 1 read!
#sample_sum_ps <- data.frame(sum = sample_sums(ps))
#summary(sample_sum_ps)
#samp0 = rownames(sample_sum_ps)[which(sample_sum_ps == '0')]
#samp1 = rownames(sample_sum_ps)[which(sample_sum_ps == '1')]

# Keep only AGFjuvs18 and Monti samples from metadata file. My Evo21 Amil as well as Monti samples in the same sequencing run
psAGF
psAGF <- subset_samples(ps.newtax, Project %in% c("AGFjuvs18"))

saveRDS(psAGF, file="psAGF.rds")
psAGF <-readRDS("psAGF.rds")

# Remove those ASVs that were not observed in any of the current samples. I seqeunced multiple datasets, from some ASVs were unique to those datasets
sum(taxa_sums(psAGF) == 0)
psAGF0 <- psAGF
psAGF <- prune_taxa(taxa_sums(psAGF) > 0, psAGF)
psAGF

#psAGF should have 59 samples. Originally 62 but deleted 3 (as shown above) due to quality
```


```{subset only sediment samples for barplot, echo = FALSE}

Treat2 <- subset_samples(psAGF, Treatment2 == "Sediment")

# Summary of read counts 
sample_sum_ps <- data.frame(sum = sample_sums(Treat2))
summary(sample_sum_ps)
samp0 = rownames(sample_sum_ps)[which(sample_sum_ps == '0')]

psAGF.nas.2 <- subset_samples(Treat2, !(rownames(sample_data(Treat2)) %in% samp0)) #should only be 30 seds
psAGF.nas.3 <- prune_samples(sample_sums(psAGF.nas.2) > 1, psAGF.nas.2) #should only be 30 seds
```


#### Variance stabilisation with DESeq2 ############################
```{transform sample counts variance stabilization, echo=F}

library(DESeq2)
# A few notes (from tutorials):

# "As input, the DESeq2 package expects count data as obtained, e.g., from RNA-seq or another
# high-throughput sequencing experiment, in the form of a matrix of integer values. The values
# in the matrix should be un-normalized counts. The DESeq2 model internally corrects for library size,
# so transformed or normalized values such as counts scaled by library size should not be used as input.

# A DESeqDataSet object must have an associated design formula. The design formula expresses the variables 
# which will be used in modeling. The formula should be a tilde (~) followed by the variables with plus 
# signs between them (it will be coerced into an formula if it is not already). The design can be changed 
# later, however then all differential analysis steps should be repeated, as the design formula is used to 
# estimate the dispersions and to estimate the log2 fold changes of the model.

# In order to benefit from the default settings of the package, you should put the variable of 
# interest at the end of the formula and make sure the control level is the first level."

# Next codes from https://github.com/joey711/phyloseq/issues/283

# Note: the function estimateSizeFactors could not work due to zero counts for some samples. That
# is why these samples were removed here from the dataset.

deseq_expdes1<-phyloseq_to_deseq2(psAGF.nas.3, ~1) 
##########or Variance stabialized transformation (VST) manually within phyloseq way described in the negative binomial tutorial:
#http://www.bioconductor.org/packages/release/bioc/vignettes/phyloseq/inst/doc/phyloseq-mixture-models.html also Deseq2 love et al. pdf
#compare different geom functions. the phyloseq one results in negative values. use Michael love's from above
#with Negative Binomial http://www.bioconductor.org/packages/release/bioc/vignettes/phyloseq/inst/doc/phyloseq-mixture-models.html
#2. geom function 2 from M.Love
counts<-counts(deseq_expdes1) #deseq object
#M.Love geomean solution
#######################################~1 with geom method M. Love
#option 1
#geoMeans = apply(counts, 1, function(row) if (all(row == 0)) 0 else exp(mean(log(row[row != 0]))))
#option 2
gm_mean = function(x, na.rm=TRUE){exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))}
#gm_mean = function(x, na.rm=TRUE){exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))}
#phyloseq geomean solution above
geoMeans = apply(counts(deseq_expdes1), 1, gm_mean) #counts function in deseq2 package
diagdds = estimateSizeFactors(deseq_expdes1, geoMeans = geoMeans)
#https://github.com/joey711/phyloseq/issues/445
hys2_TAX_subset_adultlarv_diagdds2 = DESeq(diagdds, fitType="local")

#######
#Combine previous phyloseq object with taxonomy and metadata with the new variance normalized table of ASV counts
diagvst_num.phylo<-merge_phyloseq(hys2_TAX_subset_adultlarv_diagdds2, psAGF.nas.3)
########
```

```{Final barplot of variance normalized abundances on 100% scale, echo=F}
prune_VarNorm = prune_taxa(taxa_sums(diagvst_num.phylo) > 1, diagvst_num.phylo) #393 taxa

diagvst_num.phylo.percent = transform_sample_counts(diagvst_num.phylo, function(x){x / sum(x)})

#Final barplot
p = plot_bar(diagvst_num.phylo.percent, fill="Clade")+facet_grid(.~Temp, scales="free")
p + scale_fill_manual(values=c("A"="#F6CCA0","B"="#BB8996", "C"="#616594", "D"="#0E0A0E", "F"= "#55C1E2", "I"= "white", "Unknown"= "grey"))
#deleted sample names for clutter and renamed y-axis so more clear (Variance normalized abundances in SED (%))
```

#GLM DESeq2
```{Generalized linear models and DESeq2 Benjamini-Hochberg multiple test corrections , echo=F}
#http://www.bioconductor.org/packages/release/bioc/vignettes/phyloseq/inst/doc/phyloseq-mixture-models.html
#deseq2-conversion-and-call
deseq_expdes4<-phyloseq_to_deseq2(psAGF.nas.3, ~Temp) #Treat2, ps.newtax, psAGF.nas.3
gm_mean1 = function(x, na.rm=TRUE){
  exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))
}
geoMeans2 = apply(counts(deseq_expdes4), 1, gm_mean1)
diagdds5 = estimateSizeFactors(deseq_expdes4, geoMeans = geoMeans2)
diagdds5 = DESeq(diagdds5, fitType="local")
res = results(diagdds5)
res = res[order(res$padj, na.last=NA), ]
alpha = 0.05
sigtab = res[(res$padj < alpha), ]
sigtab = cbind(as(sigtab, "data.frame"), as(tax_table(psAGF.nas.3)[rownames(sigtab), ], "matrix"))
head(sigtab)
posigtab = sigtab[sigtab[, "log2FoldChange"] > 0, ]
posigtab = posigtab[, c("baseMean", "log2FoldChange", "lfcSE", "padj", "Species2", "Clade")]
theme_set(theme_bw())
sigtabgen = subset(sigtab, !is.na(Clade))
# Phylum order
x = tapply(sigtabgen$log2FoldChange, sigtabgen$Species2, function(x) max(x))
x = sort(x, TRUE)
sigtabgen$Species2 = factor(as.character(sigtabgen$Species2), levels=names(x))
sigtabgen$Species2 = factor(as.character(sigtabgen$Species2), levels=names(x))
ggplot(sigtabgen, aes(y=Species2, x=log2FoldChange, color=Clade)) + 
  geom_vline(xintercept = 0.0, color = "gray", size = 0.5) +
  geom_point(size=6) + 
  theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5))

```


##Issues with sequencing of juveniles from SS and D1. Almost no reads


# Venn diagram, highlighting specific shared / unique taxas
```{r Venn for each group, error = FALSE, include = TRUE, echo = FALSE, fig.height= 12, fig.width= 12}

library(VennDiagram)

#using raw abundnaces with all zeros removed. Not variance normalized data

# Categories to compare
#psAGF<-ps.newtax #88 samples
psAGF<-psAGF #59 samples, pruned AGF only
Temp1 <- subset_samples(psAGF, Temp == "26C")
Temp2 <- subset_samples(psAGF, Temp == "32C")

Treat1 <- subset_samples(psAGF, Treatment2 == "C1")
Treat2 <- subset_samples(psAGF, Treatment2 == "Sediment")
Treat3 <- subset_samples(psAGF, Treatment2 == "D1")
Treat4 <- subset_samples(psAGF, Treatment2 == "SS")

# Within the groups we want to compare,
# for each OTU, sum the total across all samples in the group:
Temp1.sum <- data.frame(sum = taxa_sums(Temp1))
Temp2.sum <- data.frame(sum = taxa_sums(Temp2))

Treat1.sum <- data.frame(sum = taxa_sums(Treat1))
Treat2.sum <- data.frame(sum = taxa_sums(Treat2))
Treat3.sum <- data.frame(sum = taxa_sums(Treat3))
Treat4.sum <- data.frame(sum = taxa_sums(Treat4))

# Select taxa that occur more than zero times:
Temp1.list <- row.names(Temp1.sum)[Temp1.sum$sum>0]
Temp2.list <- row.names(Temp2.sum)[Temp2.sum$sum>0]

Treat1.list <- row.names(Treat1.sum)[Treat1.sum$sum>0]
Treat2.list <- row.names(Treat2.sum)[Treat2.sum$sum>0]
Treat3.list <- row.names(Treat3.sum)[Treat3.sum$sum>0]
Treat4.list <- row.names(Treat4.sum)[Treat4.sum$sum>0]

# Generate a list to be used in the plotting function:
candidatesTemp <- list("26 C" = Temp1.list, "32 C" = Temp2.list)
 
candidatesTreat <- list("C1" = Treat1.list, "Sediment" = Treat2.list,
                        "D1" = Treat3.list, "SS"= Treat4.list)

# Plot             
grid.draw(venn.diagram(x = candidatesTemp, filename = NULL, 
                       fill = c("#00B9E6", "#9900CC"), alpha = 0.5))

grid.draw(venn.diagram(x = candidatesTreat, filename = NULL, 
                       fill = c("#55C1E2", "#F6CCA0", "#BB8996", "#616594"), alpha = 0.5))
```

```{reblast to NCBI to check these, ECHO =F}
#Treat3.list 
[1] "AACCAATGGCCCCCTGAACGCGCATTGCACTCTTGGGACTTCCTGAGAGTATGTTTGCTTCAGTGCTTATTTTACCTCCTTGCAAGGTTCTGTCGCAACCTTGTGCCCTGGCCAGCCACGGGTTAACTTGCCCATGGCTTGCTGAGTAGTGATCTTTTAGAGCAAGCTCTGGCACGCTGTTGTTTGAGGCAGCCTATATTGAGGCTATTTCAAATGACGTTGCTACAAGCTTGATGTGTCCTTCTGCGCCGTTGCGCATCCCATAGCATGAAGTCAAACAAGAGAACCCGCTGAATTT"      
#D1

[2] "AACCAATGGCCTCCTGAACGTGCGTTGCACTCTTGGGATTTCCTGAGAGTATGTCTGCTTCAGTGCTTAACTTGCCCCAACTTTGCAAGCAGGATGTGTTTCTGCCTTGCGTTCTTATGAGCTATTGCCCTCTGAGCCAATGGCTTGTTAATTGCTTGGTTCTTGCAAAATGCTTTGCGCGCTGTTATTCAAGTTTCTACCTTCGTGGTTTTACTTGAGTGACGCTGCTCATGCTTGCAACCGCTGGGATGCAGGTGCATGCCTCTAGCATGAAGTCAGACAAGTGAACCCGCTGAATTT"
#Cladocopium sp. 2486705 isolate C12PyToKa

[3] "AACCAATGGCCTCCTGAACGTGCGTTGCACTCTTGGGATTTCCTGAGAGTATGTCTGCTTCAGTGCTTAACTTGCCCCAACTTTGCAAGCAGGATGTGTTTCTGCCTTGCGTTCTTATGAGCTATTGCCCTCTGAGCCAATTGTTAATTGCTTGGTTCTTGCAAAATGCTTTGCGCGCTGTTATTCAAGTTTCTACCTTCGTGGTTTTACTTGAGTGACGCTGCGACGCTGCTCACGCTTGCAACCGCTGGGATGCAGGTGCATGCCTCTAGCATGAAGTCAGACAAGTGAACCCGCTGAATTT"
#Symbiodinium sp. clade C isolate

####
#Treat1.list
[1] "AACCAATGGCCCCCTGAACGCGCATTGCACTCTTGGGACTTCCTGAGAGTATGTTTGCTTCAGTGCTTATTTTACCTCCTTGCAAGGTTCTGTCGCAACCTTGTGCCCTGGCCAGCCATGGGTTAACTTGCCCATGGCTTGCTGAGTAGTGATCTTTTAGAGCAAGCTCTGGCACGCTGTTGTTTGAGGCAGCCTATATTGAGGCTATTTCAAATGACGTTGCTACAAGCTTGATGTGTCCTTCTGCGCCGTTGCGCATCCCATAGCATGAAGTCAAACAAGAGAACCCGCTGAATTT"     
#Select seq MN891786.1	Durusdinium sp. isolate AC14

[2] "AACCAATGGCCTCCTGAACGTGCGTTGCACTCTTGGGATTTCCTGAGAGTATGTCTGCTTCAGTGCTTAACTTGCCCCAACTTTGCAAGCAGGATGTGTTTCTGCCTTGCGTTCTTATGAGCTATTGCCCTCTGAGCCAATGGCTTGTTAATTGCTTGGTTCTTGCAAAATGCTTTGCGCGCTGTTATTCAGGTTTCTACCTTCGTGGTTTTACTTGAGTGACGCTGCTCATGCTTGCAACCGCTGGGATGCAGGTGCATGCCTCTAGCATGAAGTCAGACAAGTGAACCCGCTGAATTT"   
#Select seq MN654288.1	Cladocopium sp. 2486705 isolate C30PyToKa

[3] "AACCAATAGGGATTTGAACGCATTCTGCGCTTTCGGGATAACCCTGAAAGCATGCCTGCTTCAGTGTCTACTGATATTTTGCCGCTGACGACATGCTCGTCGGTGTGCGTGTTTGTGTGCCAAGGTGCCCTTCTGGCCCTCGGCACATGCAGTCGACAGGAGCCTCCCCCTCAACAGGCAAACACTCGAATCACTCAGGCTGATTTTTGCGATTGCTCTGCTGTGGGTGCGCTGCTCTTGGTGGTCGTGGAGTGCCTCTCCTCTTTCAAGACATGAAGTTAGGTCAGCAAACCCGCTGAATTT"
#Select seq GU941553.1	Uncultured eukaryote clone N401T

[4] "AACCAATGGCCTCCTGAACGTGCGTTGCACTCTTGGGATTTCCTGAGAGTATGTCTGCTTCAGTGCTTAACTTGCCCCAACTTTGCAAGCAGGATGTGTTTCTGCCTTGCGTTCTTATGAGCTATTGCCCTCTGAGCCAATGGCTTGTTAATTGCTTGGTTCTTGCAAAATGCTTTGCGCGCTGTTATTCAAGTTTCTACCTTCGTGGTTTTACTTGAGTGACGCTGCTCATGCTTGCAACCGCTGGGATGCAGGTGCATGCCTCTAGCATGAAGTCAGACAAGTGAACCCGCTGAATTT"   
#Select seq MN654271.1	Cladocopium sp. 2486705 isolate C12PyToKa

[5] "AACCAATGGCCTCCTGAACGTACGTTGCACTCTTGGGATTTCCTGAGAGTATGTCTGCTTCAGTGCTTAGCTTGCCCAATCTTGCGGATAGACTTTGTTTCTGTCTTGCGCCCCTGTGAGCCATTGAGCGTCTAGCCAATGGCTTATTGAATGATTCGGTCTTGCAAAAGCTTTGCGCGCTTCTATTCAAGATTCCACCTTGGAGTGGTAATGCTTGAGTGACGCTGCTCATGCTTGCAACTGCTGGGATGCTAACGCATGCCTCTAGCATGAAGTCAGACAAGCGAACCCGCTGAATTT"   
#Select seq MK007305.1	Symbiodiniaceae sp. strain SCF 092.01

[6] "AACCAATGGCCTCCTGAACGTACGTTGCACTCTTGGGATTTCCTGAGAGTATGTCTGCTTCAGTGCTTAGCTTGCCCAATCTTGCGGATAGACTTTGTTTCTGTCTTGCGCCCCTGTGAGCCATTGAGCGTCTAGTCAATGGCTTATTGAATGATTCGGTCTTGCAAAAGCTTTGCGCGCTTCTATTCAAGATTCCACCTTGGAGTGGTATTGCTTGAGTGACGCTGCTCATGCTTGCAACTGCTGGGATGCTAACGCATGCCTCTAGCATGAAGTCAGACAAGCGAACCCGCTGAATTT"   
#Select seq MK007305.1	Symbiodiniaceae sp. strain SCF 092.01

[7] "AACCAATGGCCTCCTGAACGTACGTTGCACTCTTGGGATTTCCTGAGAGTATGTCTGCTTCAGTGCTTAGCTTGCCCAATCTTGCGGATAGATTTTGTTTCTGTCTTGCGCCCCTGTGAGCCATTGAACATCTAGTCAATGGCTTATTGAATGATTTGGTCTTGCAAAAGCTTTGCGCGCTGCTATTCAAGATTCCACCTTAAAGTGGTATTGCTTGAGTGACGCTGCTCATGCTTGCAGCTGCTGGGATGCTAGCGCATGCCTCTAGCATGAAGTCAGACAAGCGAACCCGCTGAATTT"   
#Select seq HF582847.1	Symbiodinium sp. 1363 genomic DNA containing 5.

##SS
#Treat4.list
[1] "AGCCAATGGCCCCCTGAACGCGCATTGCACTCTTGGGACTTCCTGAGAGTATGTTTGCTTCAGTGCTTATTTTACCTCCTTGCAAGGTTCTGTCGCAACCTTGTGCCCTGGCCAGCCATGGGTTAACTTGCCCATGGCTTGCTGAGTAGTGATCTTTTAGAGCAAGCTCTGGCACGCTGTTGTTTGAGGCAGCCTATATTGAGGCTATTTCAAATGACGTTGCTACAAGCTTGATGTGTCCTTCTGCGCCGTTGCGCATCCCATAGCATGAAGTCAAACAAGAGAACCCGCTGAATTT"
#Select seq MN891786.1	Durusdinium sp. isolate AC14

ss <- subset_samples(psAGF, Treatment2 == "SS")
plot_bar(ss2, fill="Clade")+facet_grid(.~Temp, scales="free")
plot(sort(taxa_sums(ss), TRUE), type="h", ylim=c(0, 50))
#as.data.frame(taxa_sums(ss))

D1 <- subset_samples(psAGF, Treatment2 == "D1a")
plot_bar(D1, fill="Clade")+facet_grid(.~Temp, scales="free")
plot(sort(taxa_sums(D1), TRUE), type="h", ylim=c(0, 50))
#as.data.frame(taxa_sums(D1))

#sediments
write.csv(Treat2.sum, "Treat2.sum.csv")
Sed <- subset_samples(psAGF, Treatment2 == "Sediment")

write.csv(Treat1.sum, "Treat1.sum.csv")
C1 <- subset_samples(psAGF, Treatment2 == "C1")
```